\documentclass{article}
\usepackage{geometry} % see geometry.pdf on how to lay out the page. There's lots.
\geometry{letterpaper} % or letter or a5paper or ... etc
% \geometry{landscape} % rotated page geometry
\RequirePackage{amsmath}
\usepackage{listings}

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{longtable}
\usepackage{hyperref}
\usepackage{color}


\title{Daily Thesis-work Report}
\author{Javier Fern\'andez}
%\date{17 de Febrero de 2009} % delete this line to display the current date

\begin{document}

\maketitle
%\newpage
%\tableofcontents
%\listoffigures
%\listoftables
%\newpage

\section{General topics addressed}
\begin{itemize}
\item Final phase implementation
\end{itemize}

\section{Spline implementation}
Using Curve API taking from \url{http://sourceforge.net/projects/curves/}\\
Given two base points and a path (including these two) a cardinal spline
is built using the CardinalSpline functionality of the library, and 
included as attribute of a EVCardinalSpline object.\\
The cardinal spline is computed and returned specifying the number of points 
to be obtained

\section{Worm Tessellation}

The FlowBasicRasterizer was deleted, adding a tesselation package. This package
contains a TriangleRasterizer class that performs the process of triangle
rasterization and shape rasterization (maybe shape will be changed). This 
hasn't been programmed yet.\\

Looking for Delaunay triangulation implementations. There are not many:
trying this one: \url{http://www.leebyron.com/else/mesh/}. The library
is called \emph{Mesh} and implements Voronoi and Delaunay triangulation.
Delaunay triangulation minimizes the minimum angle of all the angles of the 
triangles in the triangulation, they tend to avoid skinny triangles.
\url{http://en.wikipedia.org/wiki/Delaunay_triangulation}\\

\textbf{Update: }The mesh library didn't work well. Actually I have my doubts
that the Delaunay triangulation would work for what I want. It seems that
Delaunay doesn't work properly with convex polygons (shapes). A worm shape
is definitely concave ( a line between two points is not always inside the
figure).\\
\textbf{Possible solution: }Look for a polygon triangulation library/algorithm\\

This C code could be adapted: \url{http://www.flipcode.com/archives/Efficient_Polygon_Triangulation.shtml}\\
Link for different implementation ideas \url{http://www.vterrain.org/Implementation/Libs/triangulate.html}\\

\textbf{Possible library: }Poly2Tri seems to be available in Java: Library
to triangulate polygons. \url{http://code.google.com/p/poly2tri/source/checkout}
\textbf{Issues: } Couldn't get it to work properly..Didn't want to compile

\textbf{Attempt: }Reading to implement a tesselation algorithm: Put
an eye on \emph{Siedel} algorithm

\textbf{Trying Ear-snipping method from Endrov.newer.FlipCodeTessellate}:
about Ear Clipping triangulation \url{https://docs.google.com/viewer?url=http://www.geometrictools.com/Documentation/TriangulationByEarClipping.pdf}

\subsection{Final Solution}
Given clockwise generated points of the worm polygon a triangle tesselation
is created using the Ear-snipping method already implemented on
\emph{Endrov}, and the triangles are individually rasterized to obtain a list
of the points contained in the area of the worm.\\

The implementation of triangle rasterization had change due to some fundamental
implementation errors on border cases. Check \emph{week1.tex/pdf}

\section{Worm Profile}

Worm profile building ideas:
\begin{itemize}
\item Repeat the process for every isolated worm passed as a parameter
\item Find apex-base points
\item \textcolor{red}{From the apex points find the perpendicular of the rect th
at connects that current point and the previous one} Changed to skeleton points

\textbf{Option 1: the good one}
\item \textcolor{red}{The perpendicular cuts the distance transformation in two 1-pixel points
  The thickness is the half length of the line starting in one point and ending
  in the other one} Now the angle between the two segments is being calculated, and a line of half-angle is built to find the two higher cuts. The half-angle is found in the following way:
\begin{itemize}
\item Find angle from $\sigma = acos(\frac{a.b}{|a||b|})$
\item Rotate the first vector half-angle and get the parameters
  to calculate the line
\item about vectors \url{http://www.vb-helper.com/howto_find_angles.html}
\end{itemize}
\item Find an average value for every control point, and allow output of different amount of control points.

\textbf{Option 2:}
\begin{itemize}
\item The distance transformation gives the distance between the selected
pixel and the closest contour pixel. This distance is manhattan. This could
provide the radius of the circle.
\item Someway of finding the two points.
\end{itemize}


\item Building object:
  \begin{itemize}
  \item Set of control points - thickness
  \item Build a close-contour spline following thickness extreme-points
  \end{itemize}
\end{itemize}



\end{document}

